A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-05-19 paper/paper.tex
A eww arr ell

Maximum common subgraph problems come in many variants. For example, often
vertices or edges have labels (for example, denoting what kind of atom or bond they represent in
a molecule), and vertices may only be mapped to like-labelled vertices. We now
outline how to adapt \cref{McSplitAlg} to handle this and other cases.

@@

Experiments were performed on machines with dual Intel Xeon E5-2640 v2 CPUs and
64GBytes RAM. Our algorithm was implemented\footnote{URL removed for anonymous
review} in C++ and compiled using g++ 5.3.0. We compare against
the best constraint programming implementations of
\citet{DBLP:conf/cp/NdiayeS11} and \citet{DBLP:conf/cp/McCreeshNPS16} (CP-FC in
the unlabelled cases, and CP-MAC in the labelled cases, using both branching
and filtering for connected subgraphs), the clique encodings of
\citet{DBLP:conf/cp/McCreeshNPS16}, and the $k{\downarrow}$ algorithm of
\citet{UpcomingAAAIPaper} (which only supports unlabelled, undirected,
unconnected instances).  Each of these comparator programs is an optimised,
dedicated implementation and does not use a general-purpose constraint programming
toolkit.  We used the original authors' code in each case.

>>>>

Maximum common subgraph problems come in many variants. Often
vertices or edges have labels (for example, denoting the kind of atom or bond they represent in
a molecule \cite{Ehrlich:2011}), and the induced subgraphs of the two input graphs are
required to have identical labels.  Directed edges are used in an application to systems
of biochemical reactions \cite{DAM2014}.
We now outline how to adapt \cref{McSplitAlg} to handle these cases.

@@

Experiments were performed on machines with dual Intel Xeon E5-2640 v2 CPUs and
64GBytes RAM. Our algorithm was
implemented\footnote{Source code, instances, experimental scripts and raw
results are available at
https://github.com/jamestrimble/ijcai2017-partitioning-common-subgraph}
in C++ and compiled using g++ 5.3.0. We compare against the best constraint
programming implementations of \citet{DBLP:conf/cp/NdiayeS11} and
\citet{DBLP:conf/cp/McCreeshNPS16} (CP-FC in the unlabelled cases, and CP-MAC
in the labelled cases, using both branching and filtering for connected
subgraphs), the clique encodings of \citet{DBLP:conf/cp/McCreeshNPS16}, and the
$k{\downarrow}$ algorithm of \citet{UpcomingAAAIPaper} (which only supports
unlabelled, undirected, unconnected instances).  Each of these comparator
programs is an optimised, dedicated implementation and does not use a
general-purpose constraint programming toolkit.  We used the original authors'
code in each case.
